Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-11 sections/correlated-sicm-and-fm.tex
reworked (part of) the text on confocal amd SICM

So far, the combination of SICM and wide-field FM has been used to find a
region of interest such as an area containing active synapses in a culture of
a neuronal network \cite{Novak2013,Scheenen2015}
(Fig.~\ref{fig:sicm+fm}b--d). Furthermore, it has been used to first identify
primary cilia in a cell culture and subsequently use SICM to reveal whether
the selected cilium was extending into the extracellular space or was embedded
in the cell, an information which could not be retrieved by using FM alone
\cite{Zhou2018}.

@@

Similar to a SICM and wide-field combination, a combination of SICM and confocal FM enables
imaging of the same region and sample with both techniques (Fig.~\ref{fig:sicm+cfm}a). The technical
implementation involves mounting a SICM onto an inverted confocal FM. The software used to
control the two microscopes does not have to the same as both microscope record data independently 
from one another. However, as the recordings are not simultaneous, pixel-by-pixel correlation is hardly,
if at all, possible. Yet, a combination of SICM and z-stacking confocal FM yields more correlating data
than combinations of SICM and wide-field techniques as z-stacking microscopy records data points in 
multiple z planes. After imaging, these can be aligned with the SICM data and non-correlating data can be
separated from correlating data. Still, there is a potential mismatch in resolution and the data has to 
be processed after imaging to yield correlation. Yet, this implementation is suitable for all, not only 
flat, fixed samples.

SICM and confocal FM have been combined for the first time by Korchev et al \cite{Korchev2000} in
2000. The group used this combination to verify the volume measurements obtained by SICM. Just a 
year later, further development of this combination enabled simultaneous acqusition of Ca^{2+} 
imaging and topography data \cite{Shevchuk2001}. Afterwards, many different studies using a combination
of SICM and confocal FM were published:

Topographical information obtained by SICM was successfully correlated with fluorescence signals
of stained cytoskeleton molecules obtained by laser scanning confocal microscopy in platelets 
\cite{Seifert2017}.

In addition, hippocampal neurons, which are very delicate samples with many little protrusions, 
could be investigated with correlated SICM and confocal microscopy. With such a combination active
synaptic boutons could be identified \cite{Novak2013} (Fig.~\ref{fig:sicm+cfm}b) and topographical changes
in dendrites were correlated to FM data of mitochondria-containing dendrite regions \cite{Takahashi2019}.

In a study investigating the formation of human immunodeficiency virus (HIV) virus-like particles 
(VLPs) the correlated SICM-fluorescence confocal microscopy (SICM-FCM) was used to investigate 
topography changes together with die distribution of fluorescently labeled viral proteins like Gag 
or Viral Protein R (Vpr) \cite{Bednarska2020}. In contrast of investigating the virus formation 
with total internal reflection fluorescence (TIRF) microscopy \cite{Jouvenet2008} the upside 
(Oberseite?) of the cells were investigated. The release of VLPs from the upside can be a lot 
faster, than the release times that were known from TIRF measurements and difference between 
different cell types and labeled virus proteins were found \cite{Bednarska2020}.

>>>>

So far, the combination of SICM and wide-field FM has been used to find a
region of interest such as an area containing active synapses in a culture of
a neuronal network \cite{Scheenen2015} (Fig.~\ref{fig:sicm+fm}b--d) or to
identify the neuron which had been investigated by SICM-guided patch-clamp of
synaptic boutons \cite{Novak2013}.

Furthermore, it has been used to first identify primary cilia in a cell
culture and subsequently use SICM to reveal whether the selected cilium was
extending into the extracellular space or was embedded in the cell, an
information which could not be retrieved by using FM alone \cite{Zhou2018}.

@@

Similar to a SICM and wide-field combination, a combination of SICM and
confocal FM enables imaging of the same region and sample with both techniques
(Fig.~\ref{fig:sicm+cfm}a). The technical implementation involves mounting a
SICM onto an inverted confocal FM. The software used to control the two
microscopes does not have to be the same as both microscopes record data
independently from one another. However, as the recordings are not
simultaneous, pixel-by-pixel correlation is hardly, if at all, possible.

Yet,
a combination of SICM and $z$-stacking confocal FM yields more correlating
data than combinations of SICM and wide-field techniques as $z$-stacking
microscopy records data points in multiple $z$ planes. After imaging, these can
be aligned with the SICM data and non-correlating data can be separated from
correlating data. Still, there is a potential mismatch in resolution and the
data has to be processed after imaging to yield correlation. Yet, this
implementation is suitable for all, not only flat, fixed samples.

SICM and confocal FM have been combined for the first time by Korchev et al.
\cite{Korchev2000} in 2000. The group used this combination to verify the
volume measurements obtained by SICM. Just a year later, further development
of this combination enabled simultaneous acqusition of Ca\textsuperscript{2+}
imaging and topography data \cite{Shevchuk2001}.
% Afterwards, many different
% studies using a combination of SICM and confocal FM were published:

Seifert et al. \cite{Seifert2017} investigated the morphological activity of
platelets by time-lapse SICM and subsequently obtained confocal recordings of
cytoskeletal proteins of the investigated cells, allowing them to correlate
the activity of the platelets and the structure of the cytoskeleton.

SICM has been shown to allow patch-clamp recordings from tiny neuronal
structures like synaptic boutons \cite{Novak2013}. The combination of SICM and
confocal FM allowed to first record an overview image and to identify active
synaptic boutons (Fig.~\ref{fig:sicm+cfm}b), which, in a second step, could be
patch-clamped.

A second study on neurons investigated, besides others, cargo transport in
neuronal dendrites \cite{Takahashi2019}. Here, the combination of
confocal FM and SICM provided a hint that the transport processes observed by
SICM were mediated by mitochondria.

In a study investigating the formation of human immunodeficiency virus-like particles 
(VLPs) the correlated SICM-fluorescence confocal microscopy was used to investigate 
topography changes together with die distribution of fluorescently labeled viral proteins like Gag 
or Viral Protein R \cite{Bednarska2020}. In contrast to investigating the virus formation 
with TIRF microscopy \cite{Jouvenet2008}, the combination of SICM and confocal
FM allowed to investigate the apical side of the cells. It was found that the release of VLPs is a lot 
faster than the release at the basal cell side as known from TIRF
investigations and furthermore, a potential impact on the release time by the
application of a fluorescent marker was found \cite{Bednarska2020}.

% Bis hier...
